ms_figures

### 2018-01-18 man/ms_figures.Rmd
update figures

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("gridExtra")
```

@@

@@

```{r, echo=FALSE}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

@@

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=3, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9)) +
  scale_color_manual(values=c(col2005, col2012, colref))

@@

```{r, echo=FALSE}
# From explore_anomalies.Rmd 
# Read data 
anomalias_evimean <- read.csv(here("data/anomalies", "anomalias_evimean.csv"),header = TRUE, sep = ',')

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=16),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"))

@@

```{r, fig.height=9, echo=FALSE} 
grid.arrange(profile_compara, plot_sa_clu)
```

### Figure R2 = 3 
```{r, echo=FALSE}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)

>>>>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("gridExtra")
library("patchwork")
```

```{r, echo=FALSE}
show_text <- FALSE
```

```{r echo=FALSE, results='asis', eval=show_text}
cat("
# Lista de figuras

## Figure 1 Location map 
- [X] La figura 1 puede tener un mapa de localización de SN, otro de las poblaciones de roble (clasificadas por colores: cluster; y señalando las dos poblaciones muestradas en dendro). Ver MIGRAME dataset.

    - [] Ver https://github.com/ajpelu/qpyr_dendro/blob/master/out/fig/geomap/mapa_situacion.pdf 
    - Ojo con los nombres SJ (Que hacemos?)

## Figure 2. Plot combinado con EVI profile (a) y anomalías (b)
")
```

@@

Figure 1. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain range, where three cluster of oak populations have been identified [@PerezLuque2015] (showed in different colour) (b). A grid of with the MODIS pixels for each population is shown (see material and methods). Detailed location of the sampling sites: northern (San Juan, SJ) (c) and southern ones (Cáñar: CALow and CAHigh)(d). Colour Orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

```{r}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

@@

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=3, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1))) +
  scale_color_manual(values=c(col2005, col2012, colref))

@@

```{r}
# From explore_anomalies.Rmd 
# Read data 
anomalias_evimean <- read.csv(here("data/anomalies", "anomalias_evimean.csv"),header = TRUE, sep = ',')

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=16),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1)))

@@

```{r, fig.height=9} 
# grid.arrange(profile_compara, plot_sa_clu)
```

```{r, fig.height=7}
a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```

Figure 2. Profile of montly EVI values for *Q. pyrenaica* forests during the 2005 (*green*) and 2012 (*blue*) drought events and for the reference period (*gray*) (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b).

Comparison of EVI profile for the reference period (*grey*) and the 2005 (*green*) and 2012 (*blue*) drought events

### Figure R2 = 3 
```{r}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)
